---
title: "Preliminary Analyses"
#author: Drew Engelhardt
#date: March 22, 2005
output: html_document
---
```{r, include = F}
source("~/Documents/git/cjs project/cjs_cleaning.R")
library(psy)
library(broman)
library(interplot)
```

#Average Policy Differences By Race and Class
##Police Fairness Evaluations
###By race
Below I present the distribution for each of the individual police evaluation items. I include both the full sample, and then the white and black only samples respectively. Higher values denote more positive evaluations. Everything is in percentage points. I also report the results from a Chi$^2$ test on these distributions. Unsurprisingly, all of these are significant. 

Of these individual items, blacks tend to offer the most negative ratings on the *equal treatment*, *excessive force*, and *accountability* items. For whites, the distribution of repsonses to these items does not appear to meaningfully differ from the rest, at least eyeballing the results.

**Solving Crime**
```{r, echo = F}
round(prop.table(svytable(~p.crim.solve + black, d.all),2)*100)
chisq.test(round(prop.table(svytable(~p.crim.solve + black, d.all),2)*100))
```
**Protecting people like you from violent crime**
```{r, echo = F}
round(prop.table(svytable(~p.viol.crim + black, d.all), 2)*100)
chisq.test(round(prop.table(svytable(~p.viol.crim + black, d.all),2)*100))
```
**Treating racial and ethnic groups equally**
```{r, echo = F}
round(prop.table(svytable(~p.race.fair + black, d.all), 2)*100)
chisq.test(round(prop.table(svytable(~p.race.fair + black, d.all),2)*100))
```
**Not using excessive force on suspects**
```{r, echo = F}
round(prop.table(svytable(~p.exces.force + black, d.all), 2)*100)
chisq.test(round(prop.table(svytable(~p.exces.force + black, d.all),2)*100))
```
**Holding police officers accountable for misconduct**
```{r, echo = F}
round(prop.table(svytable(~p.account + black, d.all), 2)*100)
chisq.test(round(prop.table(svytable(~p.account + black, d.all),2)*100))
```

```{r, echo = F}
w.df <- subset(cjs.df, black == 0)
b.df <- subset(cjs.df, black == 1)
```
I also considered a summary evaluation index. I summed together the 5 evaluations and set the scale to run from 0-1, where higher values denote more positive evaluations. The mean for the full sample is `r myround(svymean(~police.rate.sc, d.all, na.rm = T)[[1]], 2)`, while for whites it is `r myround(svymean(~police.rate.sc, d.wht, na.rm = T)[[1]], 2)` and for blacks it is `r myround(svymean(~police.rate.sc, d.blk, na.rm = T)[[1]], 2)`. Blacks clearly rate the police on average lower than whites, and this difference is significant at p < `r myround(svyttest(police.rate.sc~black, d.all)$p.value[1], 3)`. I present the distribution for the scale for the full sample and by race below.

```{r, echo = F}
svyhist(~police.rate.sc, d.all, main = "Full Sample",
        xlab = "Police Evaluations Scale")
svyhist(~police.rate.sc, d.wht, main = "Whites Only",
        xlab = "Police Evaluations Scale")
svyhist(~police.rate.sc, d.blk, main = "Blacks Only",
        xlab = "Police Evaluations Scale")
```

It's also potentially instructive to contrast whites and blacks in how these police evaluation items scale together. To get a sense for whether these capture summary evaluations across groups, I present alphas for the 5 items scaled together. Cronbach's alpha for whites is `r myround(cronbach(cbind(w.df$p.crim.solve, w.df$p.viol.crim, w.df$p.race.fair, w.df$p.exces.force, w.df$p.account))$alpha, 2)`, while for black it is `r myround(cronbach(cbind(b.df$p.crim.solve, b.df$p.viol.crim, b.df$p.race.fair, b.df$p.exces.force, b.df$p.account))$alpha, 2)`. Although a rough pass, the similarity suggests that blacks and whites use the same dimensions to evaluate the police. I could push further on this with some factor analyses if interested.

Race seems closely related to how people evaluate the police in their area. This manifests both in individual and summary item ratings. Importantly, the dimensions on which whites and blacks evaluate the police seem to matter the same.

###By class
I created two separate measure of class based on tercile breakdowns of income and education. Each assigned repondents to an income or education tercile, however one version determined terciles based on the full weighted sample while the second looked within each racial group. Because the correlation between the two measures is `r myround(cor(cbind(cjs.df$class, cjs.df$class.rac))[2,1],2)` I use the class measure that's specific within each race to account for potential incomparabilities across groups. I again included a Chi$^2$ test for each distribution. None of these are significant. Class level does not appear to be related with evaluations of the police. Moreover, response distributions appear to be similar across items, too.

**Solving Crime**
```{r, echo = F}
round(prop.table(svytable(~p.crim.solve + class, d.all),2)*100)
chisq.test(round(prop.table(svytable(~p.crim.solve + class, d.all),2)*100))
```
**Protecting people like you from violent crime**
```{r, echo = F}
round(prop.table(svytable(~p.viol.crim + class, d.all), 2)*100)
chisq.test(round(prop.table(svytable(~p.viol.crim + class, d.all),2)*100))
```
**Treating racial and ethnic groups equally**
```{r, echo = F}
round(prop.table(svytable(~p.race.fair + class, d.all), 2)*100)
chisq.test(round(prop.table(svytable(~p.race.fair + class, d.all),2)*100))
```
**Not using excessive force on suspects**
```{r, echo = F}
round(prop.table(svytable(~p.exces.force + class, d.all), 2)*100)
chisq.test(round(prop.table(svytable(~p.exces.force + class, d.all),2)*100))
```
**Holding police officers accountable for misconduct**
```{r, echo = F}
round(prop.table(svytable(~p.account + class, d.all), 2)*100)
chisq.test(round(prop.table(svytable(~p.account + class, d.all),2)*100))
```

As for the summary evaluation index, the table below proveis the mean for each class category. Descriptively higher class individuals tend to evaluate the police more positively. A 5 point difference exists between the lowest and highest class individuals, one significant at p < `r myround(svyttest(police.rate.sc~class.rac, subset(d.all, class.rac == 0 | class.rac == 1))$p.value[[1]], 3)`.

```{r, echo = F}
CLASS <- unique(cjs.df$class.rac)
OUT <- array(NA, c(1, length(CLASS)))
colnames(OUT) <- unique(cjs.df$class.rac)
rownames(OUT) <- "mean"
for(i in 1:length(CLASS)){
  OUT[1,i] <- round(svymean(~police.rate.sc, 
            subset(d.all, class.rac == CLASS[i]), 
            na.rm = T), 2)
}
OUT
```

The plots below present the distribution of summary police evaluations for each class level. 

```{r, echo = F}
CLASS <- unique(cjs.df$class.rac)
for(i in 1:length(CLASS)){
svyhist(~police.rate.sc, 
        subset(d.all, class.rac == CLASS[i]), 
        main = paste(CLASS[i]),
        xlab = "Police Evaluations Scale")
}
```


I return to the alpha measure to contrast class category groups' police evaluations. The table below presents these tallies. No meaningful variation exists by class category, suggesting class does not shape which dimensions people rely on for evaluating the police.
```{r, echo = F}
CLASS <- unique(cjs.df$class.rac)
OUT <- array(NA, c(1, length(CLASS)))
colnames(OUT) <- unique(cjs.df$class.rac)
rownames(OUT) <- "alpha"
for(i in 1:length(CLASS)){
  c.df <- subset(cjs.df, class.rac == CLASS[i])
  OUT[1,i] <- round(cronbach(cbind(c.df$p.crim.solve, c.df$p.viol.crim, c.df$p.race.fair, c.df$p.exces.force, c.df$p.account))$alpha, 3)
}
OUT
```

To summarize, class appears unrelated to individuals' evaluations of the police. This holds for both the individual items and the summary index.

###By Race and Class
Finally, for the race and class breakdown I present the item distributions again, but by class within each racial group. I again include Chi$^2$ tests to compare the distributions. None of these tests are significant, suggesting that the intersection of race and class does not affect evaluations of the police.

**Whites: Solving Crime**
```{r, echo = F}
round(prop.table(svytable(~p.crim.solve + class, d.wht),2)*100)
chisq.test(round(prop.table(svytable(~p.crim.solve + class, d.wht),2)*100))
```
**Blacks: Solving Crime**
```{r, echo = F}
round(prop.table(svytable(~p.crim.solve + class, d.blk),2)*100)
chisq.test(round(prop.table(svytable(~p.crim.solve + class, d.blk),2)*100))
```
**Whites: Protecting people like you from violent crime**
```{r, echo = F}
round(prop.table(svytable(~p.viol.crim + class, d.wht), 2)*100)
chisq.test(round(prop.table(svytable(~p.viol.crim + class, d.wht),2)*100))
```
**Blacks: Protecting people like you from violent crime**
```{r, echo = F}
round(prop.table(svytable(~p.viol.crim + class, d.blk), 2)*100)
chisq.test(round(prop.table(svytable(~p.viol.crim + class, d.blk),2)*100))
```
**Whites: Treating racial and ethnic groups equally**
```{r, echo = F}
round(prop.table(svytable(~p.race.fair + class, d.wht), 2)*100)
chisq.test(round(prop.table(svytable(~p.race.fair + class, d.wht),2)*100))
```
**Blacks: Treating racial and ethnic groups equally**
```{r, echo = F}
round(prop.table(svytable(~p.race.fair + class, d.blk), 2)*100)
chisq.test(round(prop.table(svytable(~p.race.fair + class, d.blk),2)*100))
```
**Whites: Not using excessive force on suspects**
```{r, echo = F}
round(prop.table(svytable(~p.exces.force + class, d.wht), 2)*100)
chisq.test(round(prop.table(svytable(~p.exces.force + class, d.wht),2)*100))
```
**Blacks: Not using excessive force on suspects**
```{r, echo = F}
round(prop.table(svytable(~p.exces.force + class, d.blk), 2)*100)
chisq.test(round(prop.table(svytable(~p.exces.force + class, d.blk),2)*100))
```
**Whites: Holding police officers accountable for misconduct**
```{r, echo = F}
round(prop.table(svytable(~p.account + class, d.wht), 2)*100)
chisq.test(round(prop.table(svytable(~p.account + class, d.wht),2)*100))
```
**Blacks: Holding police officers accountable for misconduct**
```{r, echo = F}
round(prop.table(svytable(~p.account + class, d.blk), 2)*100)
chisq.test(round(prop.table(svytable(~p.account + class, d.blk),2)*100))
```

Returning to the summary evaluation index, the table below provides the means for each race/class category. Whereas the prior class-only results indicated that higher class individuals tended to evaluate the police more positively, this seems driven by whites. A 7 point difference exists between the lowest and highest class whites, but this gap is only 2 points for blacks. The former is significant at p < `r myround(svyttest(police.rate.sc~class.rac, subset(d.wht, class.rac == 0 | class.rac == 1))$p.value[[1]], 3)` while the latter is not (p = `r myround(svyttest(police.rate.sc~class.rac, subset(d.blk, class.rac == 0 | class.rac == 1))$p.value[[1]], 3)`).

```{r, echo = F}
CLASS <- unique(cjs.df$class.rac)
OUT <- array(NA, c(2, length(CLASS)))
colnames(OUT) <- unique(cjs.df$class.rac)
rownames(OUT) <- c("mean - White", "mean - Black")
for(i in 1:length(CLASS)){
  OUT[1,i] <- round(svymean(~police.rate.sc, 
            subset(d.wht, class.rac == CLASS[i]), 
            na.rm = T), 2)
  OUT[2,i] <- round(svymean(~police.rate.sc, 
            subset(d.blk, class.rac == CLASS[i]), 
            na.rm = T), 2)
}
OUT
```

Finally, I present the scale alphas in table below. The first row looks at whites across class, while the second looks at blacks by class. No meaningful variation exists according to class/race interaction, reinforcing the likelihood that people rely on the same dimensions for evaluating the police.
```{r, echo = F}
CLASS <- unique(cjs.df$class.rac)
OUT <- array(NA, c(2, length(CLASS)))
colnames(OUT) <- unique(cjs.df$class.rac)
rownames(OUT) <- c("Alpha - Whites", "Alpha - Blacks")
for(i in 1:length(CLASS)){
  wc.df <- subset(cjs.df, class.rac == CLASS[i] & black == 0)
  bc.df <- subset(cjs.df, class.rac == CLASS[i] & black == 1)
  OUT[1,i] <- round(cronbach(cbind(wc.df$p.crim.solve, wc.df$p.viol.crim, wc.df$p.race.fair, wc.df$p.exces.force, wc.df$p.account))$alpha, 3)
  OUT[2,i] <- round(cronbach(cbind(bc.df$p.crim.solve, bc.df$p.viol.crim, bc.df$p.race.fair, bc.df$p.exces.force, bc.df$p.account))$alpha, 3)
}
OUT
```

##Court Fairness
###By race
I break down each court fairness item based on the suffix. The first is whether the court will fairly apply the law, while the second two ask whether this is the case regardless of a person's class or race, resepctively. Again, I presented the response distribution in percentage points, broken down by race. The Chi$^2$ tests are again significant. Regardless of the prompt, blacks are on average less likely to think the courts in their area will be fair.

**''fairly apply the law?''**
```{r, echo = F}
round(prop.table(svytable(~court.fair + black, d.all), 2)*100)
chisq.test(round(prop.table(svytable(~court.fair + black, d.all), 2)*100))
```
**''fairly apply the law, regardless of a person's class?''**
```{r, echo = F}
round(prop.table(svytable(~court.fair.class + black, d.all), 2)*100)
chisq.test(round(prop.table(svytable(~court.fair.class + black, d.all), 2)*100))
```
**''fairly apply the law, regardless of a person's race?''**
```{r, echo = F}
round(prop.table(svytable(~court.fair.race + black, d.all), 2)*100)
chisq.test(round(prop.table(svytable(~court.fair.race + black, d.all), 2)*100))
```

We also see interesting treatment effects within racial group. While there are no differences between the baseline condition and the class prime, the race prime decreases blacks' perceptions that courts will be fair. In contrast, the same prime increases whites' perceptions of fairness. These differences are small, however. The Cohen's D effect size for whites is 0.06, whole for blacks it is 0.12. Even so, because of the divergent effects, the black-white gap in fairness evaluations grows by 5 percentage points, from 18 to 23 points.

```{r, echo = F}
summary(lm(court.fair.all ~ court.fair.treat*black, cjs.df, weights = wts_whole))
```

###By Class
Turning to class, the analyses below suggest little variation exists by class category in fairness percpetions. Moreover, this holds regardless of the prompt. Even when primed to think about class, low and high class respondents think the courts in their area will fairly apply the law.
**``fairly apply the law?''**
```{r, echo = F}
round(prop.table(svytable(~court.fair + class.rac, d.all), 2)*100)
chisq.test(round(prop.table(svytable(~court.fair + class.rac, d.all), 2)*100))
```
**``fairly apply the law, regardless of a person's class?''**
```{r, echo = F}
round(prop.table(svytable(~court.fair.class + class.rac, d.all), 2)*100)
chisq.test(round(prop.table(svytable(~court.fair.class + class.rac, d.all), 2)*100))
```
**``fairly apply the law, regardless of a person's race?''**
```{r, echo = F}
round(prop.table(svytable(~court.fair.race + class.rac, d.all), 2)*100)
chisq.test(round(prop.table(svytable(~court.fair.race + class.rac, d.all), 2)*100))
```

```{r, echo = F}
summary(lm(court.fair.all ~ court.fair.treat*class.rac, cjs.df, weights = wts_whole))
```


###By Race and Class
Finally, looking at the intersection of race and class, little variation again appears by class level. One interesting point is that for blacks, the class prime appears to have decreases the number of lower class blacks believing the courts in their area will fairly apply the law. The p-vale on the Chi$^2$ test is `r myround(chisq.test(round(prop.table(svytable(~court.fair.class + class.rac, d.blk), 2)*100))$p.value, 3)`.

**Whites: ``fairly apply the law?''**
```{r, echo = F}
round(prop.table(svytable(~court.fair + class.rac, d.wht), 2)*100)
chisq.test(round(prop.table(svytable(~court.fair + class.rac, d.wht), 2)*100))
```
**Blacks: ``fairly apply the law?''**
```{r, echo = F}
round(prop.table(svytable(~court.fair + class.rac, d.blk), 2)*100)
chisq.test(round(prop.table(svytable(~court.fair + class.rac, d.blk), 2)*100))
```
**Whites: ``fairly apply the law, regardless of a person's class?''**
```{r, echo = F}
round(prop.table(svytable(~court.fair.class + class.rac, d.wht), 2)*100)
chisq.test(round(prop.table(svytable(~court.fair.class + class.rac, d.wht), 2)*100))
```
**Blacks: ``fairly apply the law, regardless of a person's class?''**
```{r, echo = F}
round(prop.table(svytable(~court.fair.class + class.rac, d.blk), 2)*100)
chisq.test(round(prop.table(svytable(~court.fair.class + class.rac, d.blk), 2)*100))
```
**Whites: ``fairly apply the law, regardless of a person's race?''**
```{r, echo = F}
round(prop.table(svytable(~court.fair.race + class.rac, d.wht), 2)*100)
chisq.test(round(prop.table(svytable(~court.fair.race + class.rac, d.wht), 2)*100))
```
**Blacks: ``fairly apply the law, regardless of a person's race?''**
```{r, echo = F}
round(prop.table(svytable(~court.fair.race + class.rac, d.blk), 2)*100)
chisq.test(round(prop.table(svytable(~court.fair.race + class.rac, d.blk), 2)*100))
```

However, we get more nuance by looking at potential treatment effects. For whites in the class prime, higher class whites are marginally more likely to think the courts in their area are fair. The difference between low and high class whites here is 4 percentage points (p = 0.066). This is on top of a 5 point class difference in the baseline condition (p < 0.000).
```{r, echo = F}
summary(lm(court.fair.all ~ court.fair.treat*class.rac, cjs.df, weights = wts_white))
```
As for blacks, a different picture emerges. The results below show a sharp divergence in fairness evaluations by class depending on the question wording. For those receiving the class prime, higher class blacks are 9 points less likely to believe the courts in their area are fair than their lower class counterparts (p < 0.05). Interestingly, a similar effect manifests for higher class blacks receiving the race prime, although the magnitude is smaller and imprecisely estimated ($\beta = -0.07$, p < 0.1).  
```{r, echo = F}
summary(lm(court.fair.all ~ court.fair.treat*class.rac, cjs.df, weights = wts_black))
```

##Police Respect
We also asked respondents whether give the police more respect would make civilian-police interactions go more smoothly. Higher values denote a belief that being more respectful would lead to more frequent positive interactions. The crosstabs by respondent characteristics suggest that race, not class, shapes these beliefs. Blacks are much less likely than whites to beleif respect leads to consistently positive interactions. 79% of whites believe respect leads to smooth interactions "most of the time" or "always." In contrast, only 46% of blacks believe this. Consequently, the Chi$^2$ p-value by race is `r myround(chisq.test(round(prop.table(svytable(~respect.police + black, d.all), 2)*100))$p.value, 3)`. Moreover, within racial groups class does not appear to offer any variation. Perpsectives on this item thus appear to follow more from racial background than class.

###By race
```{r, echo = F}
round(prop.table(svytable(~respect.police + black, d.all), 2)*100)
chisq.test(round(prop.table(svytable(~respect.police + black, d.all), 2)*100))
```

###By Class
```{r, echo = F}
round(prop.table(svytable(~respect.police + class.rac, d.all), 2)*100)
chisq.test(round(prop.table(svytable(~respect.police + class.rac, d.all), 2)*100))
```

###By Race and Class

**Whites**
```{r, echo = F}
round(prop.table(svytable(~respect.police + class.rac, d.wht), 2)*100)
chisq.test(round(prop.table(svytable(~respect.police + class, d.wht), 2)*100))
```
**Blacks**
```{r, echo = F}
round(prop.table(svytable(~respect.police + class.rac, d.blk), 2)*100)
chisq.test(round(prop.table(svytable(~respect.police + class, d.blk), 2)*100))
```

##Police Quality "Bad Apples"
Finally, respondents reported whether or not incidents of police corruption were systemic or just "bad apples." Again, responses vary substantially by race, but not class. 34% of black respondents see these incidents as systemic issues, 23% as bad apples, and 40% a little bit of both. In contrast, 49% of whites focus on bad apples, and only 19% respond that these issues reflect systemic problems. No such variation occurs across class categories. Each class group sees a little over 40% emphasizing bad apples, with between 20 and 26% reponding that it's a systemic issue. It's interesting to note that the emphasis on systemic problems rises by class, but the overall distribution doesn't meaningfully change. 

###By race
```{r, echo = F}
round(prop.table(svytable(~pol.badapples + black, d.all), 2)*100)
chisq.test(round(prop.table(svytable(~pol.badapples + black, d.all), 2)*100))
```

###By Class
```{r, echo = F}
round(prop.table(svytable(~pol.badapples + class.rac, d.all), 2)*100)
chisq.test(round(prop.table(svytable(~pol.badapples + class.rac, d.all), 2)*100))
```

###By Race and Class
Turning to within-group differences, nothing signficantly varies. Even so, there's interesting descriptive variation within blacks. Higher class blacks are less likely to report that police corruption comes from bad apples, and are more likely to emphasize systemic issues, than are lower class blacks. The proportion reporting that both issues matter stays effectively the same.

**Whites**
```{r, echo = F}
round(prop.table(svytable(~pol.badapples + class.rac, d.wht), 2)*100)
chisq.test(round(prop.table(svytable(~pol.badapples + class, d.wht), 2)*100))
```
**Blacks**
```{r, echo = F}
round(prop.table(svytable(~pol.badapples + class.rac, d.blk), 2)*100)
chisq.test(round(prop.table(svytable(~pol.badapples + class, d.blk), 2)*100))
```


#Explaining Item Variation
##Police Fairness Evaluations
###Social Experiences
####Police Abused Friends/Family
I being by looking at whether respondents report that they or their peers had been mistreated by the police. Across all items, respondents are less positive in their evaluations of the police. Perhaps more interestingly, across all items the black-white evaluation gap closes as the frequency of mistreatment increases. The gaps remain, but they grow smaller by varying degrees.

**Solving Crime**
```{r, echo = F}
csolve.1 <- lm(p.crim.solve ~ pol.mistreat*black, data = cjs.df, weights = wts_whole)
summary(csolve.1)
interplot(csolve.1, var1 = "pol.mistreat", var2 = "black") +
  labs(title = "Racial Differences by Police Mistreatment Experience",
       x = "White vs Black",
       y = "Marginal Effect of Experiencing Police Mistreatment") +
  theme_bw()
interplot(csolve.1, var1 = "black", var2 = "pol.mistreat") +
  labs(title = "Racial Differences by Police Mistreatment Experience",
       x = "Level of Mistreatment by the Police",
       y = "Black-White Evaluation Difference") +
  theme_bw()
```

**Protecting people like you from violent crime**
```{r, echo = F}
csolve.2 <- lm(p.viol.crim ~ pol.mistreat*black, data = cjs.df, weights = wts_whole)
summary(csolve.2)
interplot(csolve.2, var1 = "pol.mistreat", var2 = "black") +
  labs(title = "Racial Differences by Police Mistreatment Experience",
       x = "White vs Black",
       y = "Marginal Effect of Experiencing Police Mistreatment") +
  theme_bw()
interplot(csolve.2, var1 = "black", var2 = "pol.mistreat") +
  labs(title = "Racial Differences by Police Mistreatment Experience",
       x = "Level of Mistreatment by the Police",
       y = "Black-White Evaluation Difference") +
  theme_bw()
```

**Treating racial and ethnic groups equally**
```{r, echo = F}
csolve.3 <- lm(p.race.fair ~ pol.mistreat*black, data = cjs.df, weights = wts_whole)
summary(csolve.3)
interplot(csolve.3, var1 = "pol.mistreat", var2 = "black") +
  labs(title = "Racial Differences by Police Mistreatment Experience",
       x = "White vs Black",
       y = "Marginal Effect of Experiencing Police Mistreatment") +
  theme_bw()
interplot(csolve.3, var1 = "black", var2 = "pol.mistreat") +
  labs(title = "Racial Differences by Police Mistreatment Experience",
       x = "Level of Mistreatment by the Police",
       y = "Black-White Evaluation Difference") +
  theme_bw()
```

**Not using excessive force on suspects**
```{r, echo = F}
csolve.4 <- lm(p.exces.force ~ pol.mistreat*black, data = cjs.df, weights = wts_whole)
summary(csolve.4)
interplot(csolve.4, var1 = "pol.mistreat", var2 = "black") +
  labs(title = "Racial Differences by Police Mistreatment Experience",
       x = "White vs Black",
       y = "Marginal Effect of Experiencing Police Mistreatment") +
  theme_bw()
interplot(csolve.4, var1 = "black", var2 = "pol.mistreat") +
  labs(title = "Racial Differences by Police Mistreatment Experience",
       x = "Level of Mistreatment by the Police",
       y = "Black-White Evaluation Difference") +
  theme_bw()
```

**Holding police officers accountable for misconduct**
```{r, echo = F}
csolve.5 <- lm(p.account ~ pol.mistreat*black, data = cjs.df, weights = wts_whole)
summary(csolve.5)
interplot(csolve.5, var1 = "pol.mistreat", var2 = "black") +
  labs(title = "Racial Differences by Police Mistreatment Experience",
       x = "White vs Black",
       y = "Marginal Effect of Experiencing Police Mistreatment") +
  theme_bw()
interplot(csolve.5, var1 = "black", var2 = "pol.mistreat") +
  labs(title = "Racial Differences by Police Mistreatment Experience",
       x = "Level of Mistreatment by the Police",
       y = "Black-White Evaluation Difference") +
  theme_bw()
```

**Summary Evaluation Index**
```{r, echo = F}
csolve.6 <- lm(police.rate.sc ~ pol.mistreat*black, data = cjs.df, weights = wts_whole)
summary(csolve.6)
interplot(csolve.6, var1 = "pol.mistreat", var2 = "black") +
  labs(title = "Racial Differences by Police Mistreatment Experience",
       x = "White vs Black",
       y = "Marginal Effect of Experiencing Police Mistreatment") +
  theme_bw()
interplot(csolve.6, var1 = "black", var2 = "pol.mistreat") +
  labs(title = "Racial Differences by Police Mistreatment Experience",
       x = "Level of Mistreatment by the Police",
       y = "Black-White Evaluation Difference") +
  theme_bw()
```

####Peers convicted of a Felony
I now turn to conditioning on whether a respondent has friends or family with felony convictions. Across all items, respondents with peers who have experienced a felony are less positive in their evaluations of the police. As with the police mistreatment item, in many cases the black-white evaluation gap closes as the number of peers with convictions increases. The gaps remain, but they grow smaller by varying degrees. Finally, relative to being mistreated by the police, the effect of social connections with felony convictions is smaller.

**Solving Crime**
```{r, echo = F}
csolve.1 <- lm(p.crim.solve ~ peer.felony*black, data = cjs.df, weights = wts_whole)
summary(csolve.1)
interplot(csolve.1, var1 = "peer.felony", var2 = "black") +
  labs(title = "Racial Differences by Peer Felony Conviction",
       x = "White vs Black",
       y = "Marginal Effect of Peer Felony Conviction") +
  theme_bw()
interplot(csolve.1, var1 = "black", var2 = "peer.felony") +
  labs(title = "Racial Differences by Peer Felony Conviction",
       x = "Peers with Felony Convictions",
       y = "Black-White Evaluation Difference") +
  theme_bw()
```

**Protecting people like you from violent crime**
```{r, echo = F}
csolve.2 <- lm(p.viol.crim ~ peer.felony*black, data = cjs.df, weights = wts_whole)
summary(csolve.2)
interplot(csolve.2, var1 = "peer.felony", var2 = "black") +
  labs(title = "Racial Differences by Peer Felony Conviction",
       x = "White vs Black",
       y = "Marginal Effect of Peer Felony Conviction") +
  theme_bw()
interplot(csolve.2, var1 = "black", var2 = "peer.felony") +
  labs(title = "Racial Differences by Peer Felony Conviction",
       x = "Peers with Felony Convictions",
       y = "Black-White Evaluation Difference") +
  theme_bw()
```

**Treating racial and ethnic groups equally**
```{r, echo = F}
csolve.3 <- lm(p.race.fair ~ peer.felony*black, data = cjs.df, weights = wts_whole)
summary(csolve.3)
interplot(csolve.3, var1 = "peer.felony", var2 = "black") +
  labs(title = "Racial Differences by Peer Felony Conviction",
       x = "White vs Black",
       y = "Marginal Effect of Peer Felony Conviction") +
  theme_bw()
interplot(csolve.3, var1 = "black", var2 = "peer.felony") +
  labs(title = "Racial Differences by Peer Felony Conviction",
       x = "Peers with Felony Convictions",
       y = "Black-White Evaluation Difference") +
  theme_bw()
```

**Not using excessive force on suspects**
```{r, echo = F}
csolve.4 <- lm(p.exces.force ~ peer.felony*black, data = cjs.df, weights = wts_whole)
summary(csolve.4)
interplot(csolve.4, var1 = "peer.felony", var2 = "black") +
  labs(title = "Racial Differences by Peer Felony Conviction",
       x = "White vs Black",
       y = "Marginal Effect of Peer Felony Conviction") +
  theme_bw()
interplot(csolve.4, var1 = "black", var2 = "peer.felony") +
  labs(title = "Racial Differences by Peer Felony Conviction",
       x = "Peers with Felony Convictions",
       y = "Black-White Evaluation Difference") +
  theme_bw()
```

**Holding police officers accountable for misconduct**
```{r, echo = F}
csolve.5 <- lm(p.account ~ peer.felony*black, data = cjs.df, weights = wts_whole)
summary(csolve.5)
interplot(csolve.5, var1 = "peer.felony", var2 = "black") +
  labs(title = "Racial Differences by Peer Felony Conviction",
       x = "White vs Black",
       y = "Marginal Effect of Peer Felony Conviction") +
  theme_bw()
interplot(csolve.5, var1 = "black", var2 = "peer.felony") +
  labs(title = "Racial Differences by Peer Felony Conviction",
       x = "Peers with Felony Convictions",
       y = "Black-White Evaluation Difference") +
  theme_bw()
```

**Summary Evaluation Index**
```{r, echo = F}
csolve.6 <- lm(police.rate.sc ~ peer.felony*black, data = cjs.df, weights = wts_whole)
summary(csolve.6)
interplot(csolve.6, var1 = "peer.felony", var2 = "black") +
  labs(title = "Racial Differences by Peer Felony Conviction",
       x = "White vs Black",
       y = "Marginal Effect of Peer Felony Conviction") +
  theme_bw()
interplot(csolve.6, var1 = "black", var2 = "peer.felony") +
  labs(title = "Racial Differences by Peer Felony Conviction",
       x = "Peers with Felony Convictions",
       y = "Black-White Evaluation Difference") +
  theme_bw()
```

###Employment
####Employed in the Government
Government-employed individuals are generally more positive in their evaluations of the police, but these differences manifest only for blacks. Black respondents still on average evaluate the police worse, but those employed in government at some level more positive in varying degrees. What varies is the effect magnitude.
**Solving Crime**
```{r, echo = F}
csolve.1 <- lm(p.crim.solve ~ employ.gov*black, data = cjs.df, weights = wts_whole)
summary(csolve.1)
interplot(csolve.1, var1 = "employ.gov", var2 = "black") +
  labs(title = "Racial Differences by Government Employment",
       x = "White vs Black",
       y = "Marginal Effect of Government Employment") +
  theme_bw()
interplot(csolve.1, var1 = "black", var2 = "employ.gov") +
  labs(title = "Racial Differences by Government Employment",
       x = "Government Employment Status",
       y = "Black-White Evaluation Difference") +
  theme_bw()
```

**Protecting people like you from violent crime**
```{r, echo = F}
csolve.2 <- lm(p.viol.crim ~ employ.gov*black, data = cjs.df, weights = wts_whole)
summary(csolve.2)
interplot(csolve.2, var1 = "employ.gov", var2 = "black") +
  labs(title = "Racial Differences by Government Employment",
       x = "White vs Black",
       y = "Marginal Effect of Government Employment") +
  theme_bw()
interplot(csolve.2, var1 = "black", var2 = "employ.gov") +
  labs(title = "Racial Differences by Government Employment",
       x = "Government Employment Status",
       y = "Black-White Evaluation Difference") +
  theme_bw()
```

**Treating racial and ethnic groups equally**
```{r, echo = F}
csolve.3 <- lm(p.race.fair ~ employ.gov*black, data = cjs.df, weights = wts_whole)
summary(csolve.3)
interplot(csolve.3, var1 = "employ.gov", var2 = "black") +
  labs(title = "Racial Differences by Government Employment",
       x = "White vs Black",
       y = "Marginal Effect of Government Employment") +
  theme_bw()
interplot(csolve.3, var1 = "black", var2 = "employ.gov") +
  labs(title = "Racial Differences by Government Employment",
       x = "Government Employment Status",
       y = "Black-White Evaluation Difference") +
  theme_bw()
```

**Not using excessive force on suspects**
```{r, echo = F}
csolve.4 <- lm(p.exces.force ~ employ.gov*black, data = cjs.df, weights = wts_whole)
summary(csolve.4)
interplot(csolve.4, var1 = "employ.gov", var2 = "black") +
  labs(title = "Racial Differences by Government Employment",
       x = "White vs Black",
       y = "Marginal Effect of Government Employment") +
  theme_bw()
interplot(csolve.4, var1 = "black", var2 = "employ.gov") +
  labs(title = "Racial Differences by Government Employment",
       x = "Government Employment Status",
       y = "Black-White Evaluation Difference") +
  theme_bw()
```

**Holding police officers accountable for misconduct**
```{r, echo = F}
csolve.5 <- lm(p.account ~ employ.gov*black, data = cjs.df, weights = wts_whole)
summary(csolve.5)
interplot(csolve.5, var1 = "employ.gov", var2 = "black") +
  labs(title = "Racial Differences by Government Employment",
       x = "White vs Black",
       y = "Marginal Effect of Government Employment") +
  theme_bw()
interplot(csolve.5, var1 = "black", var2 = "employ.gov") +
  labs(title = "Racial Differences by Government Employment",
       x = "Government Employment Status",
       y = "Black-White Evaluation Difference") +
  theme_bw()
```

**Summary Evaluation Index**
```{r, echo = F}
csolve.6 <- lm(police.rate.sc ~ employ.gov*black, data = cjs.df, weights = wts_whole)
summary(csolve.6)
interplot(csolve.6, var1 = "employ.gov", var2 = "black") +
  labs(title = "Racial Differences by Government Employment",
       x = "White vs Black",
       y = "Marginal Effect of Government Employment") +
  theme_bw()
interplot(csolve.6, var1 = "black", var2 = "employ.gov") +
  labs(title = "Racial Differences by Government Employment",
       x = "Government Employment Status",
       y = "Black-White Evaluation Difference") +
  theme_bw()
```

####Employed in the Criminal Justice System
A similar pattern holds when looking at whether or not respondents are employed in the criminal justice system. Black respondents employed in the criminal justice system evaluate the police more positively. CJS employement does not appear to have a systematic influence on whites' attitudes.
**Solving Crime**
```{r, echo = F}
csolve.1 <- lm(p.crim.solve ~ employ.cjs*black, data = cjs.df, weights = wts_whole)
summary(csolve.1)
interplot(csolve.1, var1 = "employ.cjs", var2 = "black") +
  labs(title = "Racial Differences by CJS Employment",
       x = "White vs Black",
       y = "Marginal Effect of CJS Employment") +
  theme_bw()
interplot(csolve.1, var1 = "black", var2 = "employ.cjs") +
  labs(title = "Racial Differences by CJS Employment",
       x = "CJS Employment Status",
       y = "Black-White Evaluation Difference") +
  theme_bw()
```

**Protecting people like you from violent crime**
```{r, echo = F}
csolve.2 <- lm(p.viol.crim ~ employ.cjs*black, data = cjs.df, weights = wts_whole)
summary(csolve.2)
interplot(csolve.2, var1 = "employ.cjs", var2 = "black") +
  labs(title = "Racial Differences by CJS Employment",
       x = "White vs Black",
       y = "Marginal Effect of CJS Employment") +
  theme_bw()
interplot(csolve.2, var1 = "black", var2 = "employ.cjs") +
  labs(title = "Racial Differences by CJS Employment",
       x = "CJS Employment Status",
       y = "Black-White Evaluation Difference") +
  theme_bw()
```

**Treating racial and ethnic groups equally**
```{r, echo = F}
csolve.3 <- lm(p.race.fair ~ employ.cjs*black, data = cjs.df, weights = wts_whole)
summary(csolve.3)
interplot(csolve.3, var1 = "employ.cjs", var2 = "black") +
  labs(title = "Racial Differences by CJS Employment",
       x = "White vs Black",
       y = "Marginal Effect of CJS Employment") +
  theme_bw()
interplot(csolve.3, var1 = "black", var2 = "employ.cjs") +
  labs(title = "Racial Differences by CJS Employment",
       x = "CJS Employment Status",
       y = "Black-White Evaluation Difference") +
  theme_bw()
```

**Not using excessive force on suspects**
```{r, echo = F}
csolve.4 <- lm(p.exces.force ~ employ.cjs*black, data = cjs.df, weights = wts_whole)
summary(csolve.4)
interplot(csolve.4, var1 = "employ.cjs", var2 = "black") +
  labs(title = "Racial Differences by CJS Employment",
       x = "White vs Black",
       y = "Marginal Effect of CJS Employment") +
  theme_bw()
interplot(csolve.4, var1 = "black", var2 = "employ.cjs") +
  labs(title = "Racial Differences by CJS Employment",
       x = "CJS Employment Status",
       y = "Black-White Evaluation Difference") +
  theme_bw()
```

**Holding police officers accountable for misconduct**
```{r, echo = F}
csolve.5 <- lm(p.account ~ employ.cjs*black, data = cjs.df, weights = wts_whole)
summary(csolve.5)
interplot(csolve.5, var1 = "employ.cjs", var2 = "black") +
  labs(title = "Racial Differences by CJS Employment",
       x = "White vs Black",
       y = "Marginal Effect of CJS Employment") +
  theme_bw()
interplot(csolve.5, var1 = "black", var2 = "employ.cjs") +
  labs(title = "Racial Differences by CJS Employment",
       x = "CJS Employment Status",
       y = "Black-White Evaluation Difference") +
  theme_bw()
```

**Summary Evaluation Index**
```{r, echo = F}
csolve.6 <- lm(police.rate.sc ~ employ.cjs*black, data = cjs.df, weights = wts_whole)
summary(csolve.6)
interplot(csolve.6, var1 = "employ.cjs", var2 = "black") +
  labs(title = "Racial Differences by CJS Employment",
       x = "White vs Black",
       y = "Marginal Effect of CJS Employment") +
  theme_bw()
interplot(csolve.6, var1 = "black", var2 = "employ.cjs") +
  labs(title = "Racial Differences by CJS Employment",
       x = "CJS Employment Status",
       y = "Black-White Evaluation Difference") +
  theme_bw()
```

####Criminal Justice System Profession
Finally, considering the specific position in the criminal justice system, nothing systematic appears to manifest. Some items and some occupations light up, but that varies. Moreover, nothing systematically varies between whites and blacks.

**Solving Crime**
```{r, echo = F}
csolve.1 <- lm(p.crim.solve ~ as.factor(cjs.pos)*black, data = cjs.df, weights = wts_whole)
summary(csolve.1)
# interplot(respol.1, var1 = "employ.cjs", var2 = "black") +
#   labs(title = "Racial Differences by CJS Job Status",
#        x = "White vs Black",
#        y = "Marginal Effect of having a CJS Job") +
#   theme_bw()
# interplot(respol.1, var1 = "black", var2 = "employ.cjs") +
#   labs(title = "Racial Differences by CJS Job Status",
#        x = "CJS Job Status",
#        y = "Black-White Evaluation Difference") +
#   theme_bw()
```

**Protecting people like you from violent crime**
```{r, echo = F}
csolve.2 <- lm(p.viol.crim ~ as.factor(cjs.pos)*black, data = cjs.df, weights = wts_whole)
summary(csolve.2)
# interplot(csolve.2, var1 = "employ.cjs", var2 = "black") +
#   labs(title = "Racial Differences by CJS Employment",
#        x = "White vs Black",
#        y = "Marginal Effect of CJS Employment") +
#   theme_bw()
# interplot(csolve.2, var1 = "black", var2 = "employ.cjs") +
#   labs(title = "Racial Differences by CJS Employment",
#        x = "CJS Employment Status",
#        y = "Black-White Evaluation Difference") +
#   theme_bw()
```

**Treating racial and ethnic groups equally**
```{r, echo = F}
csolve.3 <- lm(p.race.fair ~ as.factor(cjs.pos)*black, data = cjs.df, weights = wts_whole)
summary(csolve.3)
# interplot(csolve.3, var1 = "employ.cjs", var2 = "black") +
#   labs(title = "Racial Differences by CJS Employment",
#        x = "White vs Black",
#        y = "Marginal Effect of CJS Employment") +
#   theme_bw()
# interplot(csolve.3, var1 = "black", var2 = "employ.cjs") +
#   labs(title = "Racial Differences by CJS Employment",
#        x = "CJS Employment Status",
#        y = "Black-White Evaluation Difference") +
#   theme_bw()
```

**Not using excessive force on suspects**
```{r, echo = F}
csolve.4 <- lm(p.exces.force ~ as.factor(cjs.pos)*black, data = cjs.df, weights = wts_whole)
summary(csolve.4)
# interplot(csolve.4, var1 = "employ.cjs", var2 = "black") +
#   labs(title = "Racial Differences by CJS Employment",
#        x = "White vs Black",
#        y = "Marginal Effect of CJS Employment") +
#   theme_bw()
# interplot(csolve.4, var1 = "black", var2 = "employ.cjs") +
#   labs(title = "Racial Differences by CJS Employment",
#        x = "CJS Employment Status",
#        y = "Black-White Evaluation Difference") +
#   theme_bw()
```

**Holding police officers accountable for misconduct**
```{r, echo = F}
csolve.5 <- lm(p.account ~ as.factor(cjs.pos)*black, data = cjs.df, weights = wts_whole)
summary(csolve.5)
# interplot(csolve.5, var1 = "employ.cjs", var2 = "black") +
#   labs(title = "Racial Differences by CJS Employment",
#        x = "White vs Black",
#        y = "Marginal Effect of CJS Employment") +
#   theme_bw()
# interplot(csolve.5, var1 = "black", var2 = "employ.cjs") +
#   labs(title = "Racial Differences by CJS Employment",
#        x = "CJS Employment Status",
#        y = "Black-White Evaluation Difference") +
#   theme_bw()
```

**Summary Evaluation Index**
```{r, echo = F}
csolve.6 <- lm(police.rate.sc ~ as.factor(cjs.pos)*black, data = cjs.df, weights = wts_whole)
summary(csolve.6)
# interplot(csolve.6, var1 = "employ.cjs", var2 = "black") +
#   labs(title = "Racial Differences by CJS Employment",
#        x = "White vs Black",
#        y = "Marginal Effect of CJS Employment") +
#   theme_bw()
# interplot(csolve.6, var1 = "black", var2 = "employ.cjs") +
#   labs(title = "Racial Differences by CJS Employment",
#        x = "CJS Employment Status",
#        y = "Black-White Evaluation Difference") +
#   theme_bw()
```


###Racial Group Views
####Racial Resentment
**Solving Crime**
```{r, echo = F}
csolve.1 <- lm(p.crim.solve ~ rr.sc, data = cjs.df, weights = wts_white,
               subset = black == 0)
summary(csolve.1)
```

**Protecting people like you from violent crime**
```{r, echo = F}
csolve.2 <- lm(p.viol.crim ~ rr.sc, data = cjs.df, weights = wts_white,
               subset = black == 0)
summary(csolve.2)
```

**Treating racial and ethnic groups equally**
```{r, echo = F}
csolve.3 <- lm(p.race.fair ~ rr.sc, data = cjs.df, weights = wts_white,
               subset = black == 0)
summary(csolve.3)
```

**Not using excessive force on suspects**
```{r, echo = F}
csolve.4 <- lm(p.exces.force ~ rr.sc, data = cjs.df, weights = wts_white,
               subset = black == 0)
summary(csolve.4)
```

**Holding police officers accountable for misconduct**
```{r, echo = F}
csolve.5 <- lm(p.account ~ rr.sc, data = cjs.df, weights = wts_white,
               subset = black == 0)
summary(csolve.5)
```

**Summary Evaluation Index**
```{r, echo = F}
csolve.6 <- lm(police.rate.sc ~ rr.sc, data = cjs.df, weights = wts_whole,
               subset = black == 0)
summary(csolve.6)
```
####White Linked Fate

####Black Linked Fate


###Class Fragility

##Court Fairness
###Social Experiences
###Employment
###Racial Group Views
###Class Fragility
##Police Respect
###Social Experiences
####Police Abused Friends/Family
Having peers who have been mistreated by the police helps explain variation in perceptions about whether or not beleiving that respecting the police makes civilian-police interactions smoother. Mistreating by the police decreases belief that respecting the police makes interactions smoother. This works for both whites and blacks, but whites are more responsive. Moreover, the black-white gap in the outcome grows smaller as mistreatement increases.
```{r, echo = F}
respol.1 <- lm(respect.police ~ pol.mistreat*black, data = cjs.df, weights = wts_whole)
summary(respol.1)
interplot(respol.1, var1 = "pol.mistreat", var2 = "black") +
  labs(title = "Racial Differences by Police Mistreatment Experience",
       x = "White vs Black",
       y = "Marginal Effect of Experiencing Police Mistreatment") +
  theme_bw()
interplot(respol.1, var1 = "black", var2 = "pol.mistreat") +
  labs(title = "Racial Differences by Police Mistreatment Experience",
       x = "Level of Mistreatment by the Police",
       y = "Black-White Evaluation Difference") +
  theme_bw()
```

####Peers convicted of a Felony
A similar effect holds when turning to whether or not a respondent has peers with felony convictions. Here, while racial difference in responsiveness exist, the gap is smaller. Moreover, the racial gap on the outcome grows slightly smaller as peers with convictions increase.
```{r, echo = F}
respol.1 <- lm(respect.police ~ peer.felony*black, data = cjs.df, weights = wts_whole)
summary(respol.1)
interplot(respol.1, var1 = "peer.felony", var2 = "black") +
  labs(title = "Racial Differences by Peer Felony Conviction",
       x = "White vs Black",
       y = "Marginal Effect of Peer Felony Conviction") +
  theme_bw()
interplot(respol.1, var1 = "black", var2 = "peer.felony") +
  labs(title = "Racial Differences by Peer Felony Conviction",
       x = "Peers with Felony Convictions",
       y = "Black-White Evaluation Difference") +
  theme_bw()
```

###Employment
####Employed in the Government
Being employed in some level of government helps explain the black-white gap on this outcome as well. First, the marginal effect of employment is larger for blacks than whites. Second, the black-white gap grows smaller for those employed by the government.
```{r, echo = F}
respol.1 <- lm(respect.police ~ employ.gov*black, data = cjs.df, weights = wts_whole)
summary(respol.1)
interplot(respol.1, var1 = "employ.gov", var2 = "black") +
  labs(title = "Racial Differences by Government Employment",
       x = "White vs Black",
       y = "Marginal Effect of Government Employment") +
  theme_bw()
interplot(respol.1, var1 = "black", var2 = "employ.gov") +
  labs(title = "Racial Differences by Government Employment",
       x = "Government Employment Status",
       y = "Black-White Evaluation Difference") +
  theme_bw()
```

####Employed in the Criminal Justice System
A similar pattern holds when looking at variation by whether or not respondents are employed in the criminal justice system. Employment here matters solely for blacks. Employment improves perspectives on respecting the police by half a scale point. The racial gap in evaluations effectively disappears.
```{r, echo = F}
respol.1 <- lm(respect.police ~ employ.cjs*black, data = cjs.df, weights = wts_whole)
summary(respol.1)
interplot(respol.1, var1 = "employ.cjs", var2 = "black") +
  labs(title = "Racial Differences by CJS Employment",
       x = "White vs Black",
       y = "Marginal Effect of CJS Employment") +
  theme_bw()
interplot(respol.1, var1 = "black", var2 = "employ.cjs") +
  labs(title = "Racial Differences by CJS Employment",
       x = "CJS Employment Status",
       y = "Black-White Evaluation Difference") +
  theme_bw()
```

####Criminal Justice System Profession
Finally, little systematically varies by a respondent's specific position in the criminal justice system.
```{r, echo = F}
respol.1 <- lm(respect.police ~ as.factor(cjs.pos)*black, data = cjs.df, weights = wts_whole)
summary(respol.1)
# interplot(respol.1, var1 = "as.factor(cjs.pos)8", var2 = "black") +
#   labs(title = "Racial Differences by CJS Job",
#        x = "White vs Black",
#        y = "Marginal Effect of having a CJS Job: ") +
#   theme_bw()
# interplot(respol.1, var1 = "black", var2 = "cjs.pos") +
#   labs(title = "Racial Differences by CJS Job",
#        x = "CJS Job Status",
#        y = "Black-White Evaluation Difference") +
#   theme_bw()
```

###Racial Group Views
####Racial Resentment
Whites' levels of racial resentment help explain beliefs about respecting the police. Min-max changes in racial resentment amount to over a category shift in the outcome.
```{r, echo = F}
respol.1 <- lm(respect.police ~ rr_sc, data = cjs.df, weights = wts_white,
               subset = black == 0)
summary(respol.1)
```
####White Linked Fate
Whites' linked fate also helps explain the outcome, but the magnitude is small. A min-max change amounts to roughly a 1/7 a category change in the outcome.
```{r, echo = F}
respol.1 <- lm(respect.police ~ wht.lfate.sc, data = cjs.df, weights = wts_white,
               subset = black == 0)
summary(respol.1)
```
####Black Linked Fate
A similar effect holds for black linked fate. A min-max change amounts to nearly a 1/5 of a category change in the outcome.
```{r, echo = F}
respol.1 <- lm(respect.police ~ blk.lfate.sc, data = cjs.df, weights = wts_black,
               subset = black == 1)
summary(respol.1)
```
###Class Fragility
####Family class growing up
Considering variation based on family background, little varies. Blacks on average have less positive views, but nothing varies based on childhood class by either racial group.
```{r, echo = F}
respol.1 <- lm(respect.police ~ chood.class*black, data = cjs.df, weights = wts_whole)
summary(respol.1)
# interplot(respol.1, var1 = "chood.class", var2 = "black") +
#   labs(title = "Racial Differences by Childhood Class",
#        x = "White vs Black",
#        y = "Marginal Effect of Childhood Class") +
#   theme_bw()
# interplot(respol.1, var1 = "black", var2 = "chood.class") +
#   labs(title = "Racial Differences by Childhood Class",
#        x = "Income Level",
#        y = "Black-White Evaluation Difference") +
#   theme_bw()
```

####Current income
Income does more to shape perspectives on respecting the police. Income matters more among whites than blacks, with higher income whites holding more positive views about respecting the police. Income doesn't matter for blacks. Consequently, with higher income whites becoming increasingly positive, the black-white racial gap increases as income increases. 
```{r, echo = F}
respol.1 <- lm(respect.police ~ inc*black, data = cjs.df, weights = wts_whole)
summary(respol.1)
interplot(respol.1, var1 = "inc", var2 = "black") +
  labs(title = "Racial Differences by Income Level",
       x = "White vs Black",
       y = "Marginal Effect of Income Level") +
  theme_bw()
interplot(respol.1, var1 = "black", var2 = "inc") +
  labs(title = "Racial Differences by Income Level",
       x = "Income Level",
       y = "Black-White Evaluation Difference") +
  theme_bw()
```

##Police Quality "Bad Apples"
###Social Experiences
###Employment
###Racial Group Views
###Class Fragility